\Title

### 2021-06-04 manuscript/content.tex
Remove step-size coefficient from manuscript

\begin{equation}
    \mathbf{d} = \sum_{k=1}^K \alpha_k \mathbf{A}_k \mathbf{c}_k \ .
    \label{eq:gb-linear-model}
\end{equation}

@@

The gradient boosting algorithm works by fitting each component of the
additive model, one at a time, to the residuals of the previous component.
\citet{friedman2001} demonstrates that this corresponds to a steepest-descent
optimization in the so-called ``function space'', with $\alpha_k$ corresponding
to step sizes in steepest descent.
The adaptation of the gradient boosting method to find the damped least-squares
solutions for the $K$ parameters vectors $\mathbf{c}_k$ and step sizes
$\alpha_k$ in Eq.~\ref{eq:gb-linear-model} is presented in
Algorithm~\ref{alg:gradient_boosting}.

@@

    $
      \alpha_k = \underset{\alpha}{\mathrm{argmin}}
      \left(
        \left\lVert
          \mathbf{r}_{k - 1} - \alpha \mathbf{d}_k
        \right\rVert ^ 2
      \right)
      = \dfrac{
        \mathbf{r}_{k-1}\trans \mathbf{d}_k
      }{
        \mathbf{d}_k\trans \mathbf{d}_k
      }
    $
    \nllabel{alg:stepsize}
    \;

    $\mathbf{r}_k = \mathbf{r}_{k - 1} - \alpha_k\mathbf{d}_k$
    \nllabel{alg:residual}
    \;
  }
  \BlankLine
  \setstretch{1}
  \caption{Gradient boosting solution for damped least-squares regression.}
  \label{alg:gradient_boosting}
\end{algorithm}

After all $\alpha_k$ step sizes and $\mathbf{c}_k$ coefficients vectors
are estimated, we can predict the effect of the additive equivalent source
model on any point through the summation

\begin{equation}
    d(\mathbf{p}) =
    \sum\limits_{k=1}^K \sum\limits_{j=1}^{M_k}
    \alpha_k \frac{{c_k}_j}{\left\lVert \mathbf{p} - \mathbf{q}_j \right\rVert}
    \ ,
\end{equation}

@@

We can improve the efficiency of the algorithm further by using only the $N_k$ data
points that fall within the $k$-th window for fitting the sources
(steps \ref{alg:scale} and \ref{alg:fit} of
algorithm~\ref{alg:gradient_boosting}),
while using all available data when calculating the step size and residuals
(steps \ref{alg:predicted}, \ref{alg:stepsize}, and \ref{alg:residual}
of algorithm~\ref{alg:gradient_boosting}).
By doing so, we can reduce the size of the Jacobian matrix further to $N_k
\times M_k$ elements.
The forward modeling operation performed in step \ref{alg:predicted} can be
done by a summation (Eq.~\ref{eq:forward-sum})
instead of a matrix-vector product, which allows us to avoid computing and
storing the larger $N \times M_k$ Jacobian at any point.
Algorithm~\ref{alg:gradient_boosting_window} incorporates these changes and is
the final \textit{gradient-boosted equivalent source algorithm}.
Figure~\ref{fig:gradient-boosting-schematics} shows a sketch of the
gradient-boosted equivalent source algorithm with a set of observation points
that simulate a ground survey and locating one source below each data point.

@@

    $
      \alpha_k = \underset{\alpha}{\mathrm{argmin}}
      \left(
        \left\lVert
          \mathbf{r}_{k - 1} - \alpha \mathbf{d}_k
        \right\rVert ^ 2
      \right)
      = \dfrac{
        \mathbf{r}_{k-1}\trans \mathbf{d}_k
      }{
        \mathbf{d}_k\trans \mathbf{d}_k
      }
    $
    \;

    $\mathbf{r}_k = \mathbf{r}_{k - 1} - \alpha_k\mathbf{d}_k$
    \;
  }
  \BlankLine
  \setstretch{1}
  \caption{Gradient-boosted equivalent source algorithm.}
  \label{alg:gradient_boosting_window}
\end{algorithm}

@@

The influence of distance sources on the solution is maintained by using the
entire set of data points when calculating
the step size $\alpha_k$ and updating the residuals vector.
In this case, the step size prevents the algorithm from worsening the fit on
data points that fall outside of the current window.
As such, it improves the convergence of the solution and ensures that the
overall misfit decreases with iteration.

It is worth noting that two sets of equivalent sources obtained through two
adjacent overlapping windows have some portion of the sources on the same
locations, specifically the ones that fall on the intersection between the two
windows.
We can interpret this as the gradient-boosting algorithm fitting the source
coefficients multiple times: one time for every window that covers each source.
This fact can be exploited in order to save some computational memory.
Instead of storing all of the multiple $\mathbf{c}_k$ vectors
(Eq.~\ref{eq:gb-linear-model}), we can initialize a single $\mathbf{c}$ vector
with zeros, where each element represents the coefficient of each one of the
original $M$ sources.
After each iteration of the gradient-boosting algorithm, we add the
multiplication of the estimated coefficients $\hat{\mathbf{c}}_k$ and the
step-size $\alpha_k$ to the corresponding elements of vector $\mathbf{c}$.
Because the relation between the source coefficients and the effect they
generate is linear, we can safely compute the resulting field through
Equation~\ref{eq:eql-forward}.
This way, the memory needed to store the entire set of estimated coefficients
is limited to a single vector of $M$ elements.

Our gradient boosting algorithm for overlapping windows is similar to the
``bootstrap inversion'' used in \citet{vonfrese1988}, which also iteratively
fits portions of an equivalent source model to the data residuals.
The key differences are that in our method:
(i)~the sources in the overlapping portions of the windows are fitted more than
once, allowing the algorithm to self-correct for poor solutions to any given
window;
(ii)~we use only data points within the window when fitting, what enables the
use of larger datasets;
(iii)~experience shows that the step size parameter improves the convergence of
the solution, particularly when using only the data inside the windows for
fitting.

>>>>

\begin{equation}
    \mathbf{d} = \sum_{k=1}^K \mathbf{A}_k \mathbf{c}_k \ .
    \label{eq:gb-linear-model}
\end{equation}

\noindent Because of the linearity of the problem, the step-size parameters
can be included into the parameter vector $\mathbf{c}_k$.

@@

The gradient boosting algorithm works by fitting each component of the
additive model, one at a time, to the residuals of the previous component.
\citet{friedman2001} demonstrates that this corresponds to a steepest-descent
optimization in the so-called ``function space''.
The adaptation of the gradient boosting method to find the damped least-squares
solutions for the $K$ parameters vectors $\mathbf{c}_k$ in
Eq.~\ref{eq:gb-linear-model} is presented in
Algorithm~\ref{alg:gradient_boosting}.

@@

    $\mathbf{r}_k = \mathbf{r}_{k - 1} - \mathbf{d}_k$
    \nllabel{alg:residual}
    \;
  }
  \BlankLine
  \setstretch{1}
  \caption{Gradient boosting solution for damped least-squares regression.}
  \label{alg:gradient_boosting}
\end{algorithm}

After all $\mathbf{c}_k$ coefficients vectors are estimated, we can predict the
effect of the additive equivalent source model on any point through the
summation

\begin{equation}
    d(\mathbf{p}) =
    \sum\limits_{k=1}^K \sum\limits_{j=1}^{M_k}
    \frac{{c_k}_j}{\left\lVert \mathbf{p} - \mathbf{q}_j \right\rVert}
    \ ,
\end{equation}

@@

We can improve the efficiency of the algorithm further by using only the $N_k$ data
points that fall within the $k$-th window for fitting the sources
(steps \ref{alg:scale} and \ref{alg:fit} of
algorithm~\ref{alg:gradient_boosting}),
while using all available data when calculating the step size and residuals
(steps \ref{alg:predicted} and \ref{alg:residual}
of algorithm~\ref{alg:gradient_boosting}).
By doing so, we can reduce the size of the Jacobian matrix further to $N_k
\times M_k$ elements.
The forward modeling operation performed in step \ref{alg:predicted} can be
done by a summation (Eq.~\ref{eq:forward-sum})
instead of a matrix-vector product, which allows us to avoid computing and
storing the larger $N \times M_k$ Jacobian at any point.
Algorithm~\ref{alg:gradient_boosting_window} incorporates these changes and is
the final \textit{gradient-boosted equivalent source algorithm}.
Figure~\ref{fig:gradient-boosting-schematics} shows a sketch of the
gradient-boosted equivalent source algorithm with a set of observation points
that simulate a ground survey and locating one source below each data point.

@@

    $\mathbf{r}_k = \mathbf{r}_{k - 1} - \mathbf{d}_k$
    \;
  }
  \BlankLine
  \setstretch{1}
  \caption{Gradient-boosted equivalent source algorithm.}
  \label{alg:gradient_boosting_window}
\end{algorithm}

@@

It is worth noting that two sets of equivalent sources obtained through two
adjacent overlapping windows have some portion of the sources on the same
locations, specifically the ones that fall on the intersection between the two
windows.
We can interpret this as the gradient-boosting algorithm fitting the source
coefficients multiple times: one time for every window that covers each source.
This fact can be exploited in order to save some computational memory.
Instead of storing all of the multiple $\mathbf{c}_k$ vectors
(Eq.~\ref{eq:gb-linear-model}), we can initialize a single $\mathbf{c}$ vector
with zeros, where each element represents the coefficient of each one of the
original $M$ sources.
After each iteration of the gradient-boosting algorithm, we add the estimated
coefficients $\hat{\mathbf{c}}_k$ to the corresponding elements of vector
$\mathbf{c}$.
Because the relation between the source coefficients and the effect they
generate is linear, we can safely compute the resulting field through
Equation~\ref{eq:eql-forward}.
This way, the memory needed to store the entire set of estimated coefficients
is limited to a single vector of $M$ elements.

Our gradient boosting algorithm for overlapping windows is similar to the
``bootstrap inversion'' used in \citet{vonfrese1988}, which also iteratively
fits portions of an equivalent source model to the data residuals.
The key differences are that in our method:
(i)~the sources in the overlapping portions of the windows are fitted more than
once, allowing the algorithm to self-correct for poor solutions to any given
window;
(ii)~we use only data points within the window when fitting, what enables the
use of larger datasets.
